Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-02 paper/main.tex
write abstract

%###################################################################################################
\begin{abstract}
    \textbf{TODO: ABSTRACT}
    % This paper establishes the basis for a novel individual-based mechanical model of rod-shaped
    % bacteria.
    % It describes methods of how to obtain data from microscopic images such that they can be used
    % for parameter estimation purposes.
    % Furthermore, we show initial results for parameter estimates and an application of the model to
    % the formation of multilayers within bacterial colonies.
\end{abstract}

>>>>

%###################################################################################################
\begin{abstract}
    \aclp{abm} have become popular tools in the study of complex cellular systems.
    However, despite their popularity, it is often difficult to systematically estimate their
    parameters and perform advanced analyses e.g. using the profile-likelihood.
    In this work, we study the mechanical properties of rod-shaped bacteria and provide techniques
    for estimating their parameters and performing identifiability analysis on them.
    Our approach follows a blueprint of a modular framework which can be adapted to other research
    questions.
    We use time series of microscopic images as input data and incorporate advanced effects as the
    elasticity of the rod.
    The developed model serves as a generalized foundation to describe multiple species of
    rod-shaped bacteria such as \textit{E.Coli} or \textit{B.Subtilis}.
\end{abstract}
